---
title: "Assignment 2B"
author: "Majbritt Lindholt Stenbøg"
date: "3/16/2022"
output: word_document
---
## **PART A**

Upload klubbdata:
```{r}
klubbdata_edges <-  read.csv("klubbdata_edges.csv")
klubbdata_nodes <- read.csv("klubbdata_nodes.csv")
```

_Q1._
```{r, message=FALSE, warning=FALSE, results = 'hide'}
# view(klubbdata_edges)
library(igraph)
klubb_datanet = graph_from_data_frame(d=klubbdata_edges, vertices = klubbdata_nodes, directed=FALSE)
library(network)
klubb_datanet2 = network(klubbdata_edges, vertices = klubbdata_nodes, directed=FALSE)
```

_Q2._
```{r,message=FALSE, warning=FALSE, results = 'hide'}
V(klubb_datanet) # 34 actors
E(klubb_datanet) # 78 ties
```

_Q3._
```{r, message=FALSE, warning=FALSE, results = 'hide'}
library(sna)
gden(klubb_datanet2, mode = "graph") # 0.1390374
```

_Q4._
```{r, results = 'hide'}
(34-1)*0.1390374 #4.588234
```

_Q5._
```{r, results = 'hide'}
library(intergraph)
igraphklubb <- asIgraph(klubb_datanet2)
klubb_net_geoD <- geodist(klubb_datanet2)
average.path.length(igraphklubb) # 2.4082
```

_Q6._
```{r,message=FALSE, warning=FALSE, results = 'hide'}
library(dplyr)
between_klubb <- betweenness(klubb_datanet2)
Data_with_between <- cbind(klubbdata_nodes, between_klubb) # 1: 462.1428571, 34: 321.1031746
arrange(Data_with_between, between_klubb)
degree_klubb <- degree(klubb_datanet2)/2
degree_klubb # 34: 17, 1: 16

# Eigenvector centrality
evcent(klubb_datanet2, gmode="graph")
```

_Q7._
```{r, message=FALSE, warning=FALSE}
comm_klubb <- cluster_louvain(klubb_datanet, weights=NULL)
class(comm_klubb) #now it is communities
length(comm_klubb) # so it seems there are four communities
membership(comm_klubb)
modularity(comm_klubb) # 0.4188034
sizes(comm_klubb) # 1 = 12, 2 = 5, 3 = 11 and 4 = 6.
is_hierarchical(comm_klubb) # it is not hierarchical

igraph.comm_klubb <- membership(comm_klubb)

table(igraph.comm_klubb, klubbdata_nodes$faction)

library(RColorBrewer)
display.brewer.all()
colors <- brewer.pal(length(comm_klubb), 'Set3')

V(klubb_datanet)$color <- colors[membership(comm_klubb)] 

plot(klubb_datanet, vertex.label=klubbdata_nodes$faction)
```

_Q8._
```{r,message=FALSE, warning=FALSE, results = 'hide'}
cluster_klubb <- cluster_edge_betweenness(klubb_datanet)
cluster_klubb

membership(cluster_klubb)
cluster_klubb_2 <- cut_at(cluster_klubb, no = 2)
cluster_klubb_2
table(cluster_klubb_2)

assortativity(klubb_datanet, klubbdata_nodes$faction, directed=FALSE)  # 0.7434211
chisq.test(igraph.comm_klubb, klubbdata_nodes$faction) #it's significant
cor(cluster_klubb_2, klubbdata_nodes$faction) # -0.9424213 (it really cannot be in minus, so imagine it without -)

dendPlot(cluster_klubb, mode="hclust", rect = 2)
dendPlot(cluster_klubb, mode="hclust")

library(GGally)
membership_klubb <- as.factor(klubbdata_nodes$faction)

ggnet2(klubb_datanet, label= membership_klubb,color= cluster_klubb_2, palette="Set3")
```

# **Use dataset Star Wars to answer the following questions:**
```{r,message=FALSE, warning=FALSE, results = 'hide'}
library(devtools)
devtools::install_github("pj398/movienetdata")
library(movienetdata)
data("starwars_tfa", "movienetdata")
data(package = "movienetdata")
force(starwars_tfa)
```

_Q9._
```{r,message=FALSE, warning=FALSE, results = 'hide'}
library(network)
# view(starwars_tfa)

starwars_net <- network(starwars_tfa$adjacency)
summary(starwars_net)
```

_Q10._
```{r,message=FALSE, warning=FALSE, results = 'hide'}
summary(starwars_net)
```

_Q11._
```{r,message=FALSE, warning=FALSE, results = 'hide'}
gden(starwars_net, mode = "digraph") # 0.1602151
```

_Q12._
```{r,message=FALSE, warning=FALSE, results = 'hide'}
mean(degree(starwars_net))
# 9.612903
```

_Q13._
```{r,message=FALSE, warning=FALSE, results = 'hide'}
starwars_geo <- geodist(starwars_net)
mean(starwars_geo$counts) # 1.532778
```

_Q14._
```{r,message=FALSE, warning=FALSE, results = 'hide'}
between_starwars <- betweenness(starwars_net)
between_starwars
starwars_with_between <- cbind(names, between_starwars)

library(tidyverse)
# Total, in-degree and out-degree
in_degree <- degree(starwars_net, cmode="indegree")
out <- degree(starwars_net, cmode="outdegree")
total_degree <- degree(starwars_net, cmode="freeman")

# names_degree <- bind_cols(names, total_degree, in_degree, out)
# view(names_degree)

evcent(starwars_net, gmode="digraph")
```

_Q15._
```{r, message=FALSE, warning=FALSE, results = 'hide'}
get.neighborhood(starwars_net, 7) # 3  5 14 10  6
```

_Q16._
```{r,message=FALSE, warning=FALSE, results='hide'}
library(sna)

central_degree <- degree(starwars_net)
# female
node_list_starwars <-  starwars_tfa$node_list
node_list_starwars
sex_of_char <- node_list_starwars$char_female
sex_of_char_factor <- factor(sex_of_char, labels =c("Female","Other"))

palette(c("salmon","mediumseagreen"))

gplot(starwars_net, vertex.cex=central_degree, vertex.col=sex_of_char_factor, edge.col="steelblue1", label.cex = 0.9, displaylabels = TRUE, label.col="gold1", object.scale = 0.0008, arrowhead.cex=7, main= "Starwars network")
```

## **Part B**

_Create a social network (e.g. friends, relatives, classmates etc.) with at least 16 actors._
```{r,message=FALSE, warning=FALSE, results = 'hide'}
me <- graph.empty(directed = FALSE)

me <- add_vertices(
  me, 
  16, 	
  name=c("Agnes", "K","Majbritt", "Oliver", "Adam","Amalie", "Dennis", "Frederik","Nikolaj", "Caroline", "Louis","Carl","Christoffer","Simon","Rasmus","Mariella"))

me <- me + edge("K","Agnes")
me <- me + edge("K","Majbritt")
me <- me + edge("Agnes","Majbritt")
me <- me + edge("Dennis","Majbritt")
me <- me + edge("Dennis","Frederik")
me <- me + edge("Amalie","Nikolaj")
me <- me + edge("Agnes","Amalie")
me <- me + edge("K","Oliver")
me <- me + edge("Caroline","Louis")
me <- me + edge("Caroline","Majbritt")
me <- me + edge("Agnes","Adam")

me <- me + edge("Louis","Agnes")
me <- me + edge("Louis","K")
me <- me + edge("Louis","Majbritt")

me <- me + edge("Carl","Majbritt")
me <- me + edge("Carl","K")
me <- me + edge("Carl","Agnes")
me <- me + edge("Carl","Louis")
me <- me + edge("Carl","Adam")
me <- me + edge("Carl","Christoffer")

me <- me + edge("Christoffer","Majbritt")
me <- me + edge("Christoffer","Agnes")
me <- me + edge("Christoffer","K")
me <- me + edge("Christoffer","Louis")
me <- me + edge("Christoffer","Simon")
me <- me + edge("Simon","Majbritt")

me <- me + edge("Rasmus","Mariella")
me <- me + edge("Rasmus","Majbritt")

V(me) # 16
E(me) # 28
```

_Q18._
```{r, message=FALSE, warning=FALSE, results = 'hide'}
average.path.length(me)
set.seed(16)
random_graph <- rgnm(1, 16, 28, mode="graph") 
random_network <- network(random_graph, directed = FALSE)
random_igraph <- asIgraph(random_network)
average.path.length(random_igraph)
# plot(network(random_graph, directed=FALSE))
gden(random_graph, mode = "graph")
betweenness_random <- betweenness(random_graph)
#  [1] 63.000000  1.000000  0.000000  0.000000 47.333333  1.000000 30.666667 38.666667  5.000000  0.000000  8.666667 40.333333
# [13]  9.666667 28.000000 30.666667 14.000000
mean(betweenness_random)
degree_random <- degree(random_graph,gmode="graph") # 5 2 1 2 7 2 5 6 3 2 3 4 4 3 4 3
mean(degree_random)

small_world <- watts.strogatz.game(dim=1, size=16, nei=2, p=0.07)
small_world_n <- as.matrix(small_world)
small_world_n2 <-  asNetwork(small_world_n)
# plot(small_world,  layout=layout_with_kk)
gden(small_world_n2, mode = "graph")
betsworld <-  betweenness(as.matrix(get.adjacency(small_world)))
mean(betsworld)
#  [1] 23.433333 32.366667  1.166667 12.733333 16.866667 34.866667 10.700000  8.633333  8.300000  9.366667 27.700000 17.766667
# [13]  8.600000 26.200000  7.666667 11.633333
degree_world <-  degree(as.matrix(get.adjacency(small_world)),gmode="graph") # 5 5 3 4 4 5 4 4 4 4 4 4 3 4 3 4
mean(degree_world)
average.path.length(small_world)
```

_Q19._
```{r}
plot(me, vertex.size=11, main= "my friends")
plot(network(random_graph, directed=FALSE), main="Random graph")
plot(small_world, layout=layout_with_kk, main="Small world")
```

_Q20._
```{r,message=FALSE, warning=FALSE, results = 'hide'}
library(intergraph)
library(network)
me_network <- asNetwork(me)
V(me)
between_me <- betweenness(me_network)
mean(between_me)
gden(me_network, mode="graph")

total_deg_me <- degree(me_network)/2
mean(total_deg_me)
V(me)
gden(me_network, mode = "graph") #0.2333333
(16-1)*0.2333333 #3.499999

closeness_me <- closeness(me_network)
closeness_me
V(me)

evcent(me_network, gmode = "graph")
```

_a) Who you consider the key figure to contact for distributing information? Why?_
I would consider the person who is the most central person in betweenness and degree centrality (in this case, Majbritt - myself) as the key figure to contact for distributing information, as with betweenness Majbritt can react most people in the network, and also has the most edges when looking at degree, which means Majbritt has the most contacts.

_b) Who should get vaccinated first to avoid quick spreading of contagious disease? Why?_
Again Majbritt, as she has the higest betweenness and can therefore reach most people in the network compared to other people in the network. Therefore, if Majbritt gets a disease, she would reach

_Q21._
```{r}
gplot(me_network, vertex.cex=total_deg_me, vertex.col="red", edge.col="blue",displaylabels = TRUE, label.col="green", label.cex = 0.9, object.scale = 0.003, arrowhead.cex=4, main = "My friend group", usearrows=FALSE,vertex.sides = 4)
```

